Linting Linearity in Core/System FC

### 2023-01-18 report.tex
Some ideas on empty sections

\begin{itemize}
    % \item Features fundamentais
    % \item Exemplos, introduzir syntax
    \item (Ao contrário de OCaml) tem um sistema de tipos muito sofisticado
    \item Eventualmente explicação de GADTs? c/ exemplo do Vec
    \item Uma das features mais avaçadas/experimentais é o Linear Haskell
\end{itemize}

\subsection{Linear Haskell\label{linear-haskell-section}}

@@

\subsection{Core Haskell\label{core-section}}

@@

@@

@@

@@

@@

@@

They have a linearly typed something?

>>>>

% \begin{itemize}
    % \item Features fundamentais
    % \item Exemplos, introduzir syntax
    % \item (Ao contrário de OCaml) tem um sistema de tipos muito sofisticado
    % \item Eventualmente explicação de GADTs? c/ exemplo do Vec
    % \item Uma das features mais avaçadas/experimentais é o Linear Haskell
% \end{itemize}

\section{Linear Haskell\label{linear-haskell-section}}

Introduction of linear types to Haskell. How do they work, what's the syntax?
Multiplicities, examples. Monads, multiplicity polymorphism, multiplicity
polymoprhism applied to monadic bind to define resource-aware sequencing of
operations. Linear haskell relates systemFC with the linear lambda calculus?

@@

\section{Core Haskell\label{core-section}}

Haskel's intermediate representation that is statically typed

@@

The architecture of GHC
Both typecheckers, the backends Core is transformed into, and \textbf{\emph{all
core transformations}}.

@@

A brief introduction to the related work section?

@@

Haskell Core's foundational language was imbued with linear types, but it does
not account for linearity with the whole of the type system

Multiplicity annotations in SystemFC?

Rules?

@@

The paper is concerned with retrofitted lienar types but couldn't account for
optimizations in the Core. It originally did not set out to modify Core but had
to, and it's better this way bc we get optimizations typechecking safety
guarantees.

@@

Defines constraint-based type system parametrized over X which does not account
for local type refinements regarding linearity.

@@

Rust has a core based on linear types. Describe Rust's architecture?
How do they handle linearity plus optimizations
They probabluy don't typecheck linearity in Core
